\localauthor{Sebastian Vogt, Johannes Garstenauer, Johann Schicho}

\newcommand{\classtable}[1]{\begin{longtable}[H]{m{5cm}m{9cm}}
		\hline
		\textbf{Klassenname} & \textbf{Beschreibung} \\
		\hline
		\hline
		#1
	\end{longtable}
}

\newcommand{\classentry}[2]{\textbf{#1} & #2 \\
	}


\subsection{Klassendiagramm}

% Hier Klassendiagramm mal irgendwann einfügen.

\subsection{Klassenbeschreibungen}

\subsubsection{de.lases.global.transport}

\classtable{
    \classentry{Paper}{This DTO represents a paper.}
    \classentry{Privilege}{This represents a user-privilige.}
    \classentry{Review}{This DTO represents a review.}
    \classentry{ScienceField}{This DTO represents a field of Science.}
    \classentry{ScientificForum}{This DTO represents a forum}
    \classentry{Style}{This represents a user interface style.}
    \classentry{Submission}{This DTO represents a submission.}
    \classentry{SubmissionState}{This represents a submissions state.}
    \classentry{SystemSettings}{This DTO represents the system settings.}
    \classentry{User}{This DTO represents a user.}
}

\subsubsection{de.lases.global.logging}

\classtable{
	\classentry{Logging}{This Logger allows logging in different log-levels.}
}

\subsubsection{de.lases.persistence.repository}

\classtable{
	\classentry{PaperRepository}{This Repository can get the list of papers for a submission or add new ones.}

	\classentry{ScienceFieldRepository}{This Repository can get or add new fields of science from/to the database.}

	\classentry{ScientificForumRepository}{This Repository can get a list of Journals and Conferences or add new ones.}

	\classentry{SystemSettingsRepository}{This Repository can read or update the system settings.}
}

\subsubsection{de.lases.business.service}

\classtable{
    \classentry{CustomizationService}{Provides methods for the manipulation of system settings.}
    \classentry{ScienceFieldService}{Provides methods for adding and removing scientific categories.}
    \classentry{ProfileService}{Provides methods for the manipulation and removal of users.}
    \classentry{ScientificForumService}{Provides methods for the manipulation and creation of scientific forums.}
    \classentry{SubmissionLieferando}{Provides methods for delivering lists of submissions, taking into account
    their filtering, sorting and calling user.}
    \classentry{RegistrationService}{Provides methods for the creation of users.}
    \classentry{LoginService}{Provides methods for the login and logout operations.}
    \classentry{ReviewService}{Provides methods for the delivery, creation and removal of reviews.}
    \classentry{SubmissionService}{Provides methods for the delivery, creation, removal and manipulation of submissions.}
}

\subsubsection{de.lases.control.backing}
\classtable{
	\classentry{NewSubmissionBacking}{Backing bean for the page for creating a new submission.}
    \classentry{SubmissionBacking}{Backing bean for the submission page.}
    \classentry{NewReviewBacking}{Backing bean for the page for creating adding a new review.}
    \classentry{VerificationBacking}{Backing bean for the verification page.}
    \classentry{ToolbarBacking}{Backing bean for the side toolbar.}
    \classentry{NavigationBacking}{Backing bean for the navigation bar.}
    \classentry{WelcomeBacking}{Backing bean for the welcome and login page.}
    \classentry{RegistrationBacking}{Backing bean for the registration page.}
    \classentry{HomepageBacking}{Backing bean for the homepage for logged in users.}
    \classentry{NewUser}{Backing bean for the page for adding a new user.}
    \classentry{ScientificForumListBacking}{Backing bean for the list of scientific forums.}
    \classentry{UserListBacking}{Backing bean for the list of users.}
    \classentry{ResultListBacking}{Backing bean for the search result page.}
    \classentry{ScientificForumBacking}{Backing bean for the scientific forum page.}
    \classentry{NewScientificForumBacking}{Backing bean for the page for adding a new forum.}
    \classentry{ProfileBacking}{Backing bean for the profile page.}
    \classentry{AdministrationBacking}{Backing bean for the administration page.}
}

